On Secure Delegation of SampBQP with a Classical Client

### 2019-11-24 qpip.tex
Fix typo

	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-2\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref[AlgGroundStateCheck]. By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.

>>>>

	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-2\varepsilon)n$ copies out of $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}. By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.
